Title

### 2021-10-06 paper/main.tex
Up to october 5h

Umbrella sampling\cite{Torrie_1977} was used to obtain the PMF along
reaction coordinate by sampling multiple windows of $\xi$. Each sample
was obtained from a simulation where the Hamiltonian included the
following potential:

@@

where $$

\subsubsection{Well-Tempered Multiple Walker Metadynamics}

@@

\subsubsection{NAMD}

>>>>

Umbrella sampling\cite{Torrie_1977} was used to obtain the PMF along
reaction coordinate by sampling multiple windows along $\xi$. Each sample
was obtained from a simulation where the Hamiltonian included the
following potential:

@@

where

%\subsubsection{Well-Tempered Multiple Walker Metadynamics}

@@

Graphene sheets with sides of length $4.94$ and $4.87$ nm and
bond-length of $0.139$ nm were generated with VMD\cite{Humphrey_1996}
using its nanotube builder plugin.

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{/home/mbarria/Documents/Papers/graphene_adsorption_paper/figures/Graphene.png}}
\caption[]{\label{fig:system-pristine} Example of a simulated
  system. A Phenylalanine molecule is placed above a layer of pristine
  graphene inside a water-filled rectangular box. Carbon atoms are
  depicted in gray.}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{/home/mbarria/Documents/Papers/graphene_adsorption_paper/figures/Graphene_Oxide.png}}
\caption[]{\label{fig:system-oxide} (a) A simulated system where the
  graphene layer is oxidized. Carbon atoms are depicted in cyan, while
oxygen and hydrogen atoms are depicted in red and white,
respectively. (b) A section of the graphene oxide layer, showing the
distribution of the hydroxyl groups.}
\end{figure}

%\subsubsection{NAMD}
